Resource Buying Games

### 2017-02-01 slides.tex
finished conclusion and introduction

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{cancel}
\usepackage{stmaryrd}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

@@

\begin{frame}
  \frametitle{Introduction}
\end{frame}

\section{Basic Definitions}
\begin{frame}
  \frametitle{Definition: congestion model}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item $N$: set of players
    \item $E$: set of resources
    \item $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
      set of desired resources $S_{i}\subseteq E$: set of configurations
    \item $d_{i}$: demand of player $i$ for her resource
      \begin{itemize}
        \item $d_{i} = 1$ for an unweighted game
        \item $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
          in configuration $S\in\mathcal{S}$
      \end{itemize}
    \item $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
      $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
      of $S$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Definition: weighted resource buying game}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \begin{equation*}
    \leadsto\mathcal{G} = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item $\mathcal{P}=\times_{i\in N} P_{i}$ with
      $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
    \item $e\in E$ is bought under $S\in \mathcal{S}$ if
      $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
    \item $\pi_{i}(S) =
      \begin{cases}
        \sum_{e\in E}p_{i}^{e} &\textit{if }S_{i}\textit{ is bought}\\
        \infty &\textit{otherwise}
      \end{cases}$: {private cost of player $i$}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{A few simplifications}
  \begin{itemize}
    \item \emph{unweighted} games
    \item marginally non-increasing cost-function $c_{e}$:
      \begin{equation*}
        c_{e}(x + \delta) - c_{e}(x) \geq c_{e}(y + \delta) - c_{e}(y)
        \;\;x\leq y, \delta \in \mathbb{N}
      \end{equation*}
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{ln(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
    \item restrict players demands to a specific mathematical structure:
      Matroids
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Soundness}
  \begin{itemize}
    \item Termination:
      \begin{itemize}
        \item inductively applying contraction operations lead to basis
        \item deletion cannot \enquote{loose} bases for other players since
          chosen cut is inclusion-wise minimal
      \end{itemize}
    \item Correctness
      \begin{itemize}
        \item Lemma: cost of the chosen element decreases monotonically in each
          iteration
        \item assume there is a beneficial alternative basis
          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
          \begin{itemize}
            \item consider iteration $k$ in which $g$ is added to basis of $i$:
            \item if $f$ is in the corresonponding cut its cost never changes
              since it is deleted from every matroid $\rightarrow$ $f$ is not
              in the cut
            \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
              is not left in contracted matroid of $i$
            \item $f$ was deleted before (in this iteration the cost of the
              chosen element was lower than for $f$ in contradiction to lemma)
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  \frametitle{Recall: Congestion Model}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{B}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item before: $d_{i} = 1$ for all $i$
    \item now: $d_{i}\in\mathbb{N}_{>0}$ 
    \item auxiliary definitions:
      \begin{itemize}
        \item $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
        \item for a fixed $B$: $\ex_{i}\tupel{e} =
          \set{f\in E\setminus\set{e}\middle|
          (B_{i}\setminus{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
          that can replace $e$ for player $i$
        \item $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
          set of obligatory elements for at least one player
        \item $\Delta_{i}\tupel{B;e\rightarrow f} =
          c_{f}\tupel{\ell_{f}\tupel{B_{i}\cup\set{f}\setminus\set{e}}} -
          c_{f}\tupel{\ell_{f}\tupel{B}}$: marginal cost to buy resource $f$ if
          $i$ switches
        \item $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
          minimal marginal cost for exchanging $e$
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Characterisation of Pure Nash Equilibria}
  \begin{theorem}
    For a weighted matroid resource buying game
    $\tupel{N, E, \mathcal{B}, d, c}$ and $B\in\mathcal{B}$ the following
    holds: there is a payment vector $p$ such that $\tupel{B,p}$ is a
    PNE if and only if
    \begin{equation*}
      c_{e}(B) \leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
      \textit{ for all }e\in E\setminus F
    \end{equation*}
  \end{theorem}
  \begin{proof}
    if: $p_{i}^{e} =
      \begin{cases}
        \frac{\Delta_{i}^{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}\cdot
        c_{e}(B)&\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) > 0\\
        0 &\text{ otherwise}
      \end{cases}$\\
      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\
    only if: for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$
  \end{proof}
\end{frame}

\begin{frame}
  \frametitle{Existence of Pure Nash Equilibria}
  \begin{theorem}
    Every weighted matroid resource buying game with marginally non-increasing
    cost functions possesses a PNE.
  \end{theorem}
  \begin{itemize}
    \item socially optimal configuration profile: $B\in\mathcal{B}$ such that
      $\sum_{e\in E}c_{e}(\ell_{e}(B))$ is minimal
    \item for socially optimal configuration profile $B$ holds:
      \begin{equation*}
        c_{e}(B)\leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
        \text{ for all }e\in E\setminus F
      \end{equation*}
    \item for $B$ exists $p$ s.t. $\tupel{B,p}$ is a PNE
    \item (but finding socially optimal configuration profiles is NP-hard)
  \end{itemize}
\end{frame}

\section{Non-Matroid Strategy Spaces}
\begin{frame}
\frametitle{Consequences of using Non-Matroid Strategy Spaces}
  \begin{lemma}
    If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there
    exist $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
    set $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains
    $b$ and $c$. (Especially, there is $S\in\mathcal{S}$ with
    $S\subseteq X\cup Y$ and $a\in S$ but $b,c\notin S$.)
  \end{lemma}
  \begin{theorem}
    For every non-matroid anti-chain $\mathcal{S}$ on a set of resource $E$,
    there exists a weighted two-player resource buying game
    $G = \tupel{\tilde{E}, \tupel{\mathcal{S}_{1} \times
    \mathcal{S}_{2}}\times \mathcal{P}, \pi}$ having marginally non-increasing
    cost functions, whose strategy spaces $\mathcal{S}_{1}$ and
    $\mathcal{S}_{2}$ are both isomophic to $\mathcal{S}$, so that $G$ does not
    possess a pure Nash equilibrium.
  \end{theorem}
\end{frame}

\begin{frame}
  \frametitle{Construction of games without PNE}
   \begin{columns}
     \column{0.3\textwidth}
       \begin{itemize}
         \item $c_{x}(t) = t$
         \item $c_{y}(t) = 5\frac{1}{2}$
         \item $c_{z}(t) = 4$
         \item $d_{1} = 5$
         \item $d_{2} = 4$
       \end{itemize}
     \column{0.7\textwidth}
       \begin{center}
         \resizebox{\textwidth}{!}{\input{tikz/gamediagram}}
       \end{center}
   \end{columns}
   \begin{itemize}
     \item assume PNE $\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
       p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$
     \item $Z_{i}^{\ast}\subseteq\tupel{X_{i}\cup Y_{i}}$
     \item $x\not\in Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast}$
     \item $y\not\in Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}$
     \item[$\Rightarrow$] neiter $x\in Z_{1}^{\ast}$ nor $x\not\in Z_{1}^{\ast}$ $\lightning$
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Decreasing Marginal Cost Functions}
  \begin{columns}
    \column{0.5\textwidth}
      Non-Increasing Marginal Cost Functions:
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{ln(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
    \column{0.5\textwidth}
      Non-Decreasing Marginal Cost Functions:
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              xmin=1,
              xmax=4,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{5*exp(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
  \end{columns}
  \begin{theorem}
    Let $G$ be a weighted resource buying game with non-decreasing marginal
    costs and let $S^{\ast}$ be a socially optimal solution. We can compute
    (so called) marginal cost pricing vectors which induce a PNE.
  \end{theorem}
\end{frame}

\section{Conclusion}
\begin{frame}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{cancel}
\usepackage{stmaryrd}
\usepackage{url}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

@@

\begin{frame}
  \frametitle{Introduction}
    \begin{itemize}
      \item Resources: Nodes/edges in a graph, Machines to schedule jobs on,
        \dots
      \item Players: jointly buy resources to meet individual
        (potentially overlapping) demands
      \item<2-> Every player contributes to buy certain resources
      \item<3-> Payoff for a player depends on what she payed to meet her demands
        of resources
    \end{itemize}
    \uncover<4->{\begin{definition}[Pure Nash Equilibrium(informal)]
      A \emph{Pure Nash Equilibrium (PNE)} is given if for every player holds
      that, given all other players stick to their strategies, she cannot alter
      her behaviour to achieve a better payoff for herself.
    \end{definition}}
\end{frame}

\section{Basic Definitions}
\begin{frame}
  \frametitle{Definition: congestion model}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item $N$: set of players
    \item<2-> $E$: set of resources
    \item<3-> $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
      set of desired resources $S_{i}\subseteq E$: set of configurations
    \item<4-> $d_{i}$: demand of player $i$ for her resource
      \begin{itemize}
        \item<4-> $d_{i} = 1$ for an unweighted game
        \item<4-> $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
          in configuration $S\in\mathcal{S}$
      \end{itemize}
    \item<5-> $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
      $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
      of $S$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Definition: weighted resource buying game}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \begin{equation*}
    \leadsto\mathcal{G} = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item<2-> $\mathcal{P}=\times_{i\in N} P_{i}$ with
      $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
    \item<3-> $e\in E$ is bought under $S\in \mathcal{S}$ if
      $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
    \item<4-> $\pi_{i}(S) =
      \begin{cases}
        \sum_{e\in E}p_{i}^{e} &\textit{if }S_{i}\textit{ is bought}\\
        \infty &\textit{otherwise}
      \end{cases}$: {private cost of player $i$}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{A few simplifications}
  \begin{itemize}
    \item \emph{unweighted} games
    \item<2-> marginally non-increasing cost-function $c_{e}$:
      \begin{equation*}
        c_{e}(x + \delta) - c_{e}(x) \geq c_{e}(y + \delta) - c_{e}(y)
        \;\;x\leq y, \delta \in \mathbb{N}
      \end{equation*}
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{ln(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
    \item<3-> restrict players demands to a specific mathematical structure:
      Matroids
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Soundness}
  \begin{itemize}
    \item Termination:
      \begin{itemize}
        \item<2-> inductively applying contraction operations lead to basis
        \item<3-> deletion cannot \enquote{loose} bases for other players since
          chosen cut is inclusion-wise minimal
      \end{itemize}
    \item Correctness
      \begin{itemize}
        \item<4-> Lemma: cost of the chosen element decreases monotonically in each
          iteration
        \item<5-> assume there is a beneficial alternative basis
          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
          \begin{itemize}
            \item<6-> consider iteration $k$ in which $g$ is added to basis of $i$:
            \item<7-> if $f$ is in the corresonponding cut its cost never changes
              since it is deleted from every matroid $\rightarrow$ $f$ is not
              in the cut
            \item<8-> but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
              is not left in contracted matroid of $i$
            \item<9-> $f$ was deleted before (in this iteration the cost of the
              chosen element was lower than for $f$ in contradiction to lemma)
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  \frametitle{Recall: Congestion Model}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{B}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item before: $d_{i} = 1$ for all $i$
    \item<2-> now: $d_{i}\in\mathbb{N}_{>0}$ 
    \item<3-> auxiliary definitions:
      \begin{itemize}
        \item<4-> $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
        \item<5-> for a fixed $B$: $\ex_{i}\tupel{e} =
          \set{f\in E\setminus\set{e}\middle|
          (B_{i}\setminus{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
          that can replace $e$ for player $i$
        \item<6-> $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
          set of obligatory elements for at least one player
        \item<7-> $\Delta_{i}\tupel{B;e\rightarrow f} =
          c_{f}\tupel{\ell_{f}\tupel{B_{i}\cup\set{f}\setminus\set{e}}} -
          c_{f}\tupel{\ell_{f}\tupel{B}}$: marginal cost to buy resource $f$ if
          $i$ switches
        \item<8-> $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
          minimal marginal cost for exchanging $e$
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Characterisation of Pure Nash Equilibria}
  \begin{theorem}
    For a weighted matroid resource buying game
    $\tupel{N, E, \mathcal{B}, d, c}$ and $B\in\mathcal{B}$ the following
    holds: there is a payment vector $p$ such that $\tupel{B,p}$ is a
    PNE if and only if
    \begin{equation*}
      c_{e}(B) \leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
      \textit{ for all }e\in E\setminus F
    \end{equation*}
  \end{theorem}
  \begin{proof}
    if: \uncover<2->{$p_{i}^{e} =
      \begin{cases}
        \frac{\Delta_{i}^{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}\cdot
        c_{e}(B)&\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) > 0\\
        0 &\text{ otherwise}
      \end{cases}$\\
      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\}
    only if: \uncover<3->{for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$}
  \end{proof}
\end{frame}

\begin{frame}
  \frametitle{Existence of Pure Nash Equilibria}
  \begin{theorem}
    Every weighted matroid resource buying game with marginally non-increasing
    cost functions possesses a PNE.
  \end{theorem}
  \begin{itemize}
    \item<2-> socially optimal configuration profile: $B\in\mathcal{B}$ such that
      $\sum_{e\in E}c_{e}(\ell_{e}(B))$ is minimal
    \item<3-> for socially optimal configuration profile $B$ holds:
      \begin{equation*}
        c_{e}(B)\leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
        \text{ for all }e\in E\setminus F
      \end{equation*}
    \item<4-> for $B$ exists $p$ s.t. $\tupel{B,p}$ is a PNE
    \item<5-> (but finding socially optimal configuration profiles is NP-hard)
  \end{itemize}
\end{frame}

\section{Non-Matroid Strategy Spaces}
\begin{frame}
\frametitle{Consequences of using Non-Matroid Strategy Spaces}
  \begin{lemma}
    If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there
    exist $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
    set $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains
    $b$ and $c$. (Especially, there is $S\in\mathcal{S}$ with
    $S\subseteq X\cup Y$ and $a\in S$ but $b,c\notin S$.)
  \end{lemma}
  \uncover<2->{\begin{theorem}
    For every non-matroid anti-chain $\mathcal{S}$ on a set of resource $E$,
    there exists a weighted two-player resource buying game
    $G = \tupel{\tilde{E}, \tupel{\mathcal{S}_{1} \times
    \mathcal{S}_{2}}\times \mathcal{P}, \pi}$ having marginally non-increasing
    cost functions, whose strategy spaces $\mathcal{S}_{1}$ and
    $\mathcal{S}_{2}$ are both isomophic to $\mathcal{S}$, so that $G$ does not
    possess a pure Nash equilibrium.
  \end{theorem}}
\end{frame}

\begin{frame}
  \frametitle{Construction of games without PNE}
   \begin{columns}
     \column{0.3\textwidth}
       \begin{itemize}
         \item $c_{x}(t) = t$
         \item $c_{y}(t) = 5\frac{1}{2}$
         \item $c_{z}(t) = 4$
         \item $d_{1} = 5$
         \item $d_{2} = 4$
       \end{itemize}
     \column{0.7\textwidth}
       \begin{center}
         \resizebox{\textwidth}{!}{\input{tikz/gamediagram}}
       \end{center}
   \end{columns}
   \begin{itemize}
     \item<2-> assume PNE $\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
       p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$
     \item<3-> $Z_{i}^{\ast}\subseteq\tupel{X_{i}\cup Y_{i}}$
     \item<4-> $x\not\in Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast}$
     \item<5-> $y\not\in Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}$
     \item<6->[$\Rightarrow$] neiter $x\in Z_{1}^{\ast}$ nor $x\not\in Z_{1}^{\ast}$ $\lightning$
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Decreasing Marginal Cost Functions}
  \begin{columns}
    \column{0.5\textwidth}
      Non-Increasing Marginal Cost Functions:
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{ln(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
    \column{0.5\textwidth}
      Non-Decreasing Marginal Cost Functions:
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              xmin=1,
              xmax=4,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{5*exp(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
  \end{columns}
  \uncover<2->{\begin{theorem}
    Let $G$ be a weighted resource buying game with non-decreasing marginal
    costs and let $S^{\ast}$ be a socially optimal solution. We can compute
    (so called) marginal cost pricing vectors which induce a PNE.
  \end{theorem}}
\end{frame}

\section{Conclusion}
\begin{frame}
  \frametitle{Results}
  \begin{itemize}
    \item Resource Buying Games
    \item<2-> Matroids:
      \parbox{6cm}{
        \begin{itemize}
          \item Operations: Contraction, Deletion
          \item Cuts
        \end{itemize}
      }
    \item<3-> Games:
      \parbox{8cm}{
        \begin{itemize}
          \item \parbox{6cm}{
              \begin{tabular}{|l|ll|}
                \hline
                Non-increasing marginal & Matroid & No Matroid\\\hline
                unweighted & Algorithm & \\
                weighted & PNE & No PNE\\\hline
                Non-decreasing marginal & PNE & \\\hline
              \end{tabular}
            }
        \end{itemize}
      }
    \item<4-> Slides: \url{github.com/weltoph/sem-alg-gametheory}
  \end{itemize}
  \uncover<5->{\centering Thank you for your attention!}
\end{frame}
